Adaptive broadcast tree for multicores

### 2013-05-02 paper.tex
Added new numbers

In Figure~\ref{fig:mst_gruyere_operations}, we visualize sending of a
broadcast message in \naive order. We use the MST given in
Figure~\ref{fig:mst_gruyere}.  When core 08 sends its six messages, it
does so in random order (here: in increasing node ID order). This is
inefficient, as the latency of the broadcast is dominated by cores 12,
24 and 28 rather than cores 9, 10 and 11. A better schedule for
sending messages to the children of core 8 would be to start with the
child from which the longest path emerges.

@@

@@

\begin{table}[htb]
  \centering
  \begin{tabular}{llll}
    \toprule
    topology & scheduling & time & factor \\
    \midrule
    MST & naive         & 241 & 1.00 \\
    MST & longest first & 151 & 0.63 \\
    \bottomrule
  \end{tabular}
  \caption{Simulation results for simplified machine model}
  \label{tab:sim_results}
\end{table}

>>>>

In Figure~\ref{fig:mst_gruyere_operations}, we visualize sending of a
broadcast message in \naive order. We use the MST given in
Figure~\ref{fig:mst_gruyere}.  When core 08 sends its six messages, it
does so in random order (here: in increasing node ID order). This is
inefficient, as the latency of the broadcast is dominated by cores 12,
24 and 28 rather than cores 9, 10 and 11.

@@

A better schedule for sending messages to the children of core 8 would
be to start with the child from which the longest path emerges.

\stefan{TODO: write down algorithm}

@@

\begin{table}[htb]
  \centering
  \begin{tabular}{llll}
    \toprule
    topology & scheduling & time & factor \\
    \midrule
    MST & naive                     & 241 & 1.00 \\
    MST & highest link weight first & 151 & 0.63 \\
    MST & longest path first        & 151 & 0.63 \\
    \bottomrule
  \end{tabular}
  \caption{Simulation results for simplified machine model}
  \label{tab:sim_results}
\end{table}

Scheduling based on the longest path does not make a difference for
the current MST, but will be better in many cases. \stefan{We need to
  find a model where this is actually true. But we also need to
  evaluate if the increase in complexity is worth it}
